\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Edward Q. Zou} \\ \vspace{1pt}
    \small \href{mailto:eddiezou7374@gmail.com}{\underline{eddiezou7374@gmail.com}} $|$ 
    \href{https://linkedin.com/in/edward-zou-13bb77182}{\underline{LinkedIn}} $|$
    \href{https://github.com/ezouu}{\underline{GitHub}} $|$
    \href{https://edwardportfolio-lyart.vercel.app/}{\underline{Portfolio}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California Santa Cruz}{Santa Cruz, CA}
      {Bachelor of Science in Computer Science; GPA: 3.86 (Dean’s Honors List)}{Aug. 2022 -- Present}
    \resumeSubheading
      {Mission San Jose High School}{Fremont, CA}
      {High School Diploma; SAT: 1510 (Math: 800, Reading: 710)}{Aug. 2018 -- May 2022}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://github.com/ezouu/cfe}{\underline{\textbf{CFE Environment}}}}{2024 -- Present}
      \resumeItemListStart
        \resumeItem{Developed CPU initialization and bootstrap code for use on processors like the STM32 and its derivatives.}
        \resumeItem{Implemented functions to initialize CPUs, caches, memory controllers, and peripherals.}
        \resumeItem{Developed and optimized ARM assembly code for the STM32, integrating into hardware peripherals.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://github.com/ezouu/ezouu.github.io}{\underline{\textbf{My Portfolio Website}}}}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{Developed a personal portfolio to showcase projects and professional experiences.}
        \resumeItem{Implemented responsive design and interactive elements using HTML, CSS, and JavaScript.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://github.com/ezouu/stock-market-game}{\underline{\textbf{Stock Market Game}}}}{2022 -- 2023}
      \resumeItemListStart
        \resumeItem{Developed Stock Market Game that allows user to login and perform trades using artificial currency.}
        \resumeItem{Makes use of data from Yahoo Finance to pull live data to simulate the actual stock market.}
        \resumeItem{Used React and Highcharts to represent data pulled, coded website in JS and HTML.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Teacher/Tutor}{June 2018 -- Present}
      {All Star Institute}{Fremont, CA}
      \resumeItemListStart
        \resumeItem{Taught 100+ students through private and group tutoring in all areas of the sciences.}
        \resumeItem{Taught classes on Java, Python, as well as Geometry/Algebra 2 to competitive mathematics (AMC 8, 10, 12).}
        \resumeItem{Currently teaching math olympiad and python in person.}
      \resumeItemListEnd

    \resumeSubheading
      {Teacher's Assistant}{Aug. 2021 -- Jun. 2022}
      {University of California Santa Cruz}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Assisted preparing Labs, Exams, homework, study material, and grading assignments for 153 students.}
        \resumeItem{Helped specific students with learning issues to understand concepts and improve their grades.}
        \resumeItem{Hosted office hours and private tutoring sessions.}
      \resumeItemListEnd

    \resumeSubheading
      {Dining Hall Worker}{June 2023 -- Present}
      {UCSC Cowell/Stevenson Dining Hall}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Performed a variety of semi-skilled and skilled food preparations, serving, maintenance, and safety and sanitation functions.}
        \resumeItem{Maintained a smooth and efficient workflow while working in a team environment.}
      \resumeItemListEnd

    \resumeSubheading
      {President/Founder}{August 2023 -- Present}
      {UCSC Poker Club}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Founded UCSC poker, organized tournaments and educational sessions with professional player mentors.}
        \resumeItem{Grew the club to 200+ members, both students and locals.}
        \resumeItem{Held weekly meetings dedicated to studying probability and practicing games/tournaments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, HTML/CSS/JS/React, Linux, Assembly, C, C++} \\
     \textbf{Tools}{: Solidworks, Fusion360, Photoshop, Lightroom, Final Cut, Adobe Premiere Pro} \\
     \textbf{Other}{: Digital and Film (35mm) Photography}
    }}
 \end{itemize}

\end{document}
